---
title: "wx_2011"
output: html_document
---

Here, we create a sample dataset.

```{r message = FALSE}
library(dplyr)
library(lubridate)
library(devtools)
```

Load our data and take a look:

```{r}
wx_inst <- readRDS("obs_wx_inst.Rds")

glimpse(wx_inst)
```

We want only from the year 2011, and only these variables:

* `instant` datetime of the observation
* `tmp_db` dry-bulb temperature (°C)
* `tmp_wb` wet-bulb temperature (°C)
* `rel_humid` relative humidity (1)
* `p_sl` sea-level pressure (Pa)

Apparently, attributes don't sit well with `dplyr`. There has to be a better way to do this, but I'll do it by hand for now.

```{r}
wx_2011 <- wx_inst %>%
  select(instant, tmp_db, tmp_wb, rel_humid, p_sl) 

attributes(wx_2011$tmp_db) <- NULL
attributes(wx_2011$tmp_wb) <- NULL
attributes(wx_2011$rel_humid) <- NULL
attributes(wx_2011$p_sl) <- NULL

wx_2011 <- wx_2011 %>%
  filter(year(instant) == 2011)

glimpse(wx_2011)
```

Now, we have a dataset that we can add to the package:

```{r}
use_data(wx_2011, pkg = "..", overwrite = TRUE)
```