---
title: "Coefficients"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r message = FALSE}
library(ggvis)
library(dplyr)
library(lubridate)
library(groundTemp)
```

The first step of the ground-temperature modeling process is to fit a sinusoid to an air-temperature dataset. This gives us a model for the surface temperature.

The form of the sinusoid:

\[T(t, 0) = {T_0} + \Delta {T_0}\sin \left( {\frac{{2\pi (t - {t_0})}}{{\Delta {t_0}}} - \frac{\pi }{2}} \right)\]

Symbol   | Description            | Units
:-------: | :--------------       | :----
$T$      | Temperature            | °C   
$T_0$      | Temperature, annual mean            | °C   
$\Delta T_0$      | Temperature, annual amplitude            | °C   
$t$      | time, from 1970-01-01 UTC | s
$t_0$    | time when surface-temperature is at its minimum | s 
$\Delta t_0$    | duration of a tropical year | s 

Here's a year of temperature data:

```{r}
ggvis_temp <- 
  wx_2011 %>%
  ggvis(x = ~instant, y = ~tmp_db) %>%
  layer_points(fill := "blue", fillOpacity := 0.1, size := 20) 
  

ggvis_temp
```

Let's get the coefficients:

```{r}
surface_temp_coef <- surface_temp_coef(wx_2011$instant, wx_2011$tmp_db)

surface_temp_coef
```

Here it is, as a table:

Symbol | Name | Value
------:|:-----|:-----
$T_0$  | `temp_ref` | `r surface_temp_coef$temp_ref`
$\Delta T_0$ | `dtemp_ref` | `r surface_temp_coef$dtemp_ref`
$t_0$ | `time_ref` | `r surface_temp_coef$time_ref`

We can now use this information to estimate and plot the surface temperature. We will make a function, for now, but we will show how do build the function in a later vignette.

```{r}
surface_temp <- function(instant){
  
  dtime <- as.numeric(instant) - as.numeric(surface_temp_coef$time_ref)
  
  phase <- 2*pi*dtime/tropical_year$dtime_ref - pi/2 
  
  surface_temp_coef$temp_ref +
    surface_temp_coef$dtemp_ref*sin(phase)
  
}

df_surface <- 
  data_frame(
    instant = ymd("2011-01-01", tz = "America/New_York") + seq(0, 365)*ddays(1),
    tmp_db = surface_temp(instant)
  )
```

We superimpose the line for the surface-temperature model.

```{r}
ggvis_temp %>%
  layer_paths(stroke := "red", strokeWidth := 2, data = df_surface) 
```

Now that we have the coefficients for the surface-temperature, the next step is to incorporate the thermal-diffusivity of the ground-material.
